Estimating Correspondences of Deformable Objects ``In-the-wild"

### 2015-11-06 contents/evaluation.tex
Updates from ShareLaTeX

\paragraph{Databases \& Error Metrics} In the case of face, we build both models using the 811 training images of the Labelled Faces Parts in-the-Wild (LFPW) \cite{belhumeur2013localizing}. Sparse AAMs were built from the 68 points annotations provided by~\cite{sagonas_iccv_300w_2013}. Our dAAMs were built as described in Step~\ref{sec:step4}. In both cases we build the appearance models using pixel intensities. The results are reported on the 224 images of the LFPW testset.

In the case of the ear, given the lack of publicly available annotated databases, we collected 605 high resolution images from the internet, that were captured under unconstrained conditions. The images were manually annotated with respect to a 55 point sparse annotation mark-up, as well as the curve annotations proposed in this paper. Examples of these two type of ear annotations are shown in Figure \ref{fig:intro}. We randomly split the database into two disjoint sets of training (500) and testing (105) images. The training of the two models was done in the same way as in the face's case.

@@

\paragraph{Results} Cumulative Error Distribution (CED) curves for this experiment are shown in Figure \ref{fig:daam_benchmark}. We can readily observe that the accuracy achieved by ear models, in terms of the previous normalised point-to-point error measure, is lower than the one achieved by face models. This result is expected due to the more complex structure of the ear shape. Through visual inspection we determined that fitting errors below 0.1 for ears typically look plausible under the previous error measure where fitting errors below 0.6 for faces. Results show that, for this experiment, the fitting accuracy achieved by our dAAMs is marginally better to the one achieved by classic AAMs using intensity representations. In fact, classic AAM fail to improve the accuracy of the original initialisation on ears. Therefore the propose pipeline is capable of dealing with the complex structure of non-rigid shapes and learn dAAMs from simple curve line annotations that can compete and even surpass (in the case of a simple pixel intensity image representation) classic AAM, build from carefully annotated point landmarks, is quite remarkable.

>>>>

\paragraph{Databases \& Error Metrics} In the case of face, we build both models using the 811 training images of the Labelled Faces Parts in-the-Wild (LFPW) \cite{belhumeur2013localizing}. Sparse AAMs were built from the 68 points annotations provided by~\cite{sagonas_iccv_300w_2013}. Our dAAMs were built as described in Step~\ref{sec:step4}. In both cases we build the appearance models using pixel intensities. The results are reported on the 224 images of the LFPW testset. The fitting error is evaluated as the point-to-point distance normalised by the face's size.

In the case of the ear, given the lack of publicly available annotated databases, we collected 605 high resolution images from the internet, that were captured under unconstrained conditions. The images were manually annotated with respect to a 55 point sparse annotation mark-up, as well as the curve annotations proposed in this paper. Examples of these two type of ear annotations are shown in Figure \ref{fig:intro}. We randomly split the database into two disjoint sets of training (500) and testing (105) images. The training and evaluation of the two models is done in the same way as in the face's case.

@@

\paragraph{Results} We report the results in Figure \ref{fig:daam_benchmark} using Cumulative Error Distribution (CED) curves.

Through visual inspection we determined that fitting errors below 0.1 typically look plausible under the previous error measure where fitting errors below 0.6 for faces. Results show that, for this experiment, the fitting accuracy achieved by our dAAMs is marginally better to the one achieved by classic AAMs using intensity representations. In fact, classic AAM fail to improve the accuracy of the original initialisation on ears. Therefore the propose pipeline is capable of dealing with the complex structure of non-rigid shapes and learn dAAMs from simple curve line annotations that can compete and even surpass (in the case of a simple pixel intensity image representation) classic AAM, build from carefully annotated point landmarks, is quite remarkable.
